% ACKNOWLEGDEMENTS

\thispagestyle{empty}

\begin{center}

\Large{\underline{\textbf{ACKNOWLEDGEMENT}}}\\

\end{center}

\vspace{1cm}

\noindent
We would like to express our sincere gratitude to \textbf{\guidename} for his invaluable guidance and support throughout our project. His expertise has been instrumental in our success. We are truly grateful for his contributions and the knowledge we have gained under his mentorship.

\vspace{0.5cm}

\noindent
We are also grateful to \textbf{\director}, Director, School of Sciences,
\textbf{Dr. K. N. Varalakshmi}, Director, Centre for Research in Pure \& Applied Sciences and
\textbf{Dr. K. R. Sridhara Murthi}, Director of Academics \& Planning, JAIN (Deemed-to-be
University) for providing us with this opportunity. We are thankful to \textbf{Dr. N. Shanthi},
Head of the Department of Physics and Electronics and \textbf{Dr. S. Thiyagaraj}, Programme-
Head, M. Sc. Programme, for their constant support and encouragement.

\vspace{0.5cm}

\noindent
We thank \textbf{Dr. Chenraj Roychand}, Chancellor, \textbf{Dr. N. Sundararajan},
Pro-Chancellor and \textbf{Dr. Raj Singh}, Vice-Chancellor, JAIN (Deemed-to-be University), for
providing the required infrastructure and support without which this project would not have
been possible.

\vspace{0.5cm}

\noindent
We are grateful to all the faculty members, Mr. Arvind Krishnapur, Physics lab technician and Mr. Rajesh, Physics lab assistant for their kind support towards us.

\vspace{1.5cm}

\noindent
\begin{minipage}{0.5\textwidth}

(\authone)

\vspace{1.5cm}

(\authtwo)

\end{minipage}%
\begin{minipage}{0.5\textwidth}
\flushright

\textbf{June, 2023\\
Bengaluru}
\end{minipage}